Naturalness in U(1) extensions of the MSSM

### 2015-01-20 paper/e6ssm-tuning-paper.tex
moved around some details about plots and changed caption. still working on this.

To further illustrate point we looked at how the tuning compares for a
low tuning benchmarks in the MSSM and E6SSM when the highscale
boundary condition, $M_X$ is raised.  The results of this are shown in
Fig.~\ref{Fig:BMs-varyMX} where in the top panel we see that in this
case the dependence of the E6SSM tuning on the cutoff is rather
complicated leading, such that any statement about which model is more
tuned depends on the cutoff scale considered.

@@

\begin{figure}
\begin{center}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_mssm_cutoff_scan_3_points_tuning_plot.png}} 
\resizebox{!}{5.5cm}{%
\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}} 
\\
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_mssm_mixing_small_M3_all_tuning_data.png}}%%
\caption{Top Panel: Scatter plot of fine tuning vs high scale $M_X$ for benchmark points given in (?).  Left Panel: Individual sensitivites of E6SSM BM plotted against the high scale $M_X$.  Right Panel: Individual sensitivites of MSSM BM plotted against the high scale $M_X$.    }
\label{Fig:BMs-varyMX}
\end{center}
\end{figure}

>>>>

To further illustrate point we looked at how the tuning compares for
low tuning benchmarks in the MSSM and E6SSM when the highscale
boundary condition, $M_X$ is raised.

The results of this are shown in
Fig.~\ref{Fig:BMs-varyMX} where in the top left panel we see that the
dependence of the E6SSM tuning on the cutoff is rather complicated
leading, such that any statement about which model is more tuned
depends on the cutoff scale considered.

E$_6$SSM BM1

@@

\begin{figure}
\begin{center}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_mssm_cutoff_scan_3_points_tuning_plot.png}} 
\resizebox{!}{5.5cm}{%
\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}} 
\\
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_mssm_mixing_small_M3_all_tuning_data.png}}%%
\caption{{\bf Top left panel:} Scatter plot of fine tuning vs high scale $M_X$ for the three benchmark points given in (?).  {\bf Top right panel:}  Individual sensitivites of MSSM BM plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.  {\bf Bottom left Panel:} Individual sensitivites of E6SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.  {\bf Bottom right Panel:}Individual sensitivites of E6SSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.    }
\label{Fig:BMs-varyMX}
\end{center}
\end{figure}
